### 2020-02-13 README.Rmd
Added outline for remainder of code

>>>>

### Model specification

* Model formula: Growth as a function of

* `get_model_specs()`. Inputs:
    + define identification/grouping classification
    + `growth_df` format
* `create_focal_and_comp()`. Inputs:
    + `growth_df`
    + `max_dist`: who are your competitors
    + `model_specs`: grouping of competitor biomasses

### Model fit and prediction

* `fit_bayesian_model()`. 
    + Inputs: `focal_and_comp`, `model_specs`
    + Output: `posterior_param`
* `predict_bayesian_model()`. 
    + Inputs: `focal_and_comp`, `model_specs`, `posterior_param`
    + Output: `focal_and_comp` with updated `growth_hat` variable
* Show observed vs predicted growth
* CV: `run_cv()` is a wrapper to `fit_bayesian_model()` and `predict_bayesian_model()`. 
* Permutation test:
  + Add line to that shuffles competitor species within `focal_and_comp` just before fitting model
  + permutation AND CV: add `run_shuffle` argument to `run_cv()`

### Model output and performance

* Make plot posterior parameter functions
